Building the Mega Single Cell Transcriptome Ocular Meta-Atlas

### 2021-07-25 manuscript_01_gigascience_resubmission.Rmd
table tweaks, text tweaks

The set of Snakemake pipelines that takes in the raw fastq sequence and outputs the scEiaD is at https://github.com/davemcg/scEiad [@kosterSnakemakeScalableBioinformatics2012]. The publication commit is #ffdf738. Furthermore, the repository has been deposited at Zenodo under 10.5281/zenodo.4638117 We will briefly discuss the pipeline choices, programs and algorithms, and versions below. For the R packages, we provide package versions as the supplementary file "R_session_info.txt"

We have deposited the 10x (v2) fastq files for our iPSC-based RPE data in GEO at accession GSE180662. We give download links for the count matrices, seurat and anndata objects, cell level metadata, and our codebases in `supTab_cap(name = 'supTab_links', display = 'cite')`.

@@

# Supplemental Information
## Tables
```{r supTab1_CTcounts, fig.width=4, fig.height=14, out.width=300, echo = F, results='asis', warning = F, fig.cap = supTab1_CTcounts_cap, fig.pos = 'H'}
supTab1_CTcounts_cap <- supTab_cap(name='supTab1_CTcounts', caption =  'Counts for cell type labels. Published are the author created labels from the published datasets. Transferred are the cell labels that were transferred by our xgboost-based machine learning model onto the entire scEiaD dataset.')
cat("<div id=\"tbl:supTab1_CTcounts\">")
source('figs_and_tables/sup_fig__xgboost_PR.R')
source('figs_and_tables/sup_fig2__celltype_xgboost_labelling.R')
fontsize(ctTable  %>% padding(padding = 0, part = "body") %>% align(align = 'center', part = 'all') %>% autofit(), size = 8, part = 'all')
#Output Caption (* * for italics)
cat(paste0("\n*",supTab1_CTcounts_cap,"*\n"))
# Output </div>
cat("</div>")
```

@@

```{r supTab_SAcounts, fig.width=5, fig.height=14, out.width=300, fig.cap=supTab_SAcounts_cap, echo=FALSE, results='asis', message = FALSE, warning = FALSE}
cat("<div id=\"tbl:supTab_SAcounts\">")
supTab_SAcounts_cap <- supTab_cap(name='supTab_SAcounts', caption =  'Counts for number of studies with cell types labels before and after cell type label transfer')

fontsize(saTable  %>% padding(padding = 0, part = "body") %>% align(align = 'center', part = 'all') %>% autofit(), size = 8, part = 'all') 
#Output Caption (* * for italics)
cat(paste0("\n*",supTab_SAcounts_cap,"*\n"))
# Output </div>
cat("</div>")
```

```{r supTab_links, fig.width=2, fig.height=6, out.width=300, echo = F, results='asis', warning = F, fig.cap = supTab_links_cap, fig.pos = 'H'}
supTab_links_cap <- supTab_cap(name='supTab_links', caption =  'Links to code and resources')
cat("<div id=\"tbl:supTab_links\">")

linksTable <- tibble::tribble(
                                           ~`Resource or File`,                                                                         ~Link,  ~Accession,
                                             "Seurat Object", "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/scEiaD_all_seurat_v3.Rdata",          NA,
                                            "Anndata Object",    "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/scEiaD_all_anndata.h5ad",          NA,
                                   "Counts, R sparse matrix",               "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/counts.Rdata",          NA,
                                       "Cell level metadata",     "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/metadata_filter.tsv.gz",          NA,
                              "Codebase for scEiaD creation",                                           "https://github.com/davemcg/scEiaD",   "ffdf738",
                            "Codebase for scEiad manuscript",                                "https://github.com/davemcg/scEiaD_manuscript",          NA,
                "Zenodo deposit of all above files and code",                                                      "10.5281/zenodo.4638117",   "4638117",
                            "iPSC RPE scRNA Raw Fastq Files",                "https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE180662", "GSE180662"
                )
fontsize(flextable(linksTable)  %>% padding(padding = 0, part = "body") %>% align(align = 'left', part = 'all') %>% autofit(), size = 4, part = 'all')
#Output Caption (* * for italics)
cat(paste0("\n*",supTab_links_cap,"*\n"))
# Output </div>
cat("</div>")
```

>>>>

The set of Snakemake pipelines that takes in the raw fastq sequence and outputs the scEiaD is at https://github.com/davemcg/scEiad [@kosterSnakemakeScalableBioinformatics2012]. The publication commit is #ffdf738. Furthermore, the repository has been deposited at Zenodo under 10.5281/zenodo.5129265 We will briefly discuss the pipeline choices, programs and algorithms, and versions below. For the R packages, we provide package versions as the supplementary file "R_session_info.txt"

We have deposited the 10x (v2) fastq files for our iPSC-based RPE data in GEO at accession GSE180662. We give download links for the count matrices, seurat and anndata objects, cell level metadata, and our codebases in `r supTab_cap(name = 'supTab_links', display = 'cite')`.

@@

# Supplemental Information
## Tables
```{r supTab1_CTcounts, fig.width=4, fig.height=14, out.width=300, echo = F, results='asis', warning = F, fig.cap = supTab1_CTcounts_cap, fig.pos = 'H'}
supTab1_CTcounts_cap <- supTab_cap(name='supTab1_CTcounts', caption =  'Counts for cell type labels. Published are the author created labels from the published datasets. Transferred are the cell labels that were transferred by our xgboost-based machine learning model onto the entire scEiaD dataset.')
cat("<div id=\"tbl:supTab1_CTcounts\">")
suppressMessages( source('figs_and_tables/sup_fig__xgboost_PR.R'))
suppressMessages( source('figs_and_tables/sup_fig2__celltype_xgboost_labelling.R'))
fontsize(ctTable  %>% padding(padding = 0, part = "body") %>% align(align = 'center', part = 'all') %>% autofit(), size = 8, part = 'all') %>% fit_to_width(7)
#Output Caption (* * for italics)
cat(paste0("\n*",supTab1_CTcounts_cap,"*\n"))
# Output </div>
cat("</div>")
```

@@

```{r supTab_SAcounts, fig.width=6, fig.height=14, out.width=300, fig.cap=supTab_SAcounts_cap, echo=FALSE, results='asis', message = FALSE, warning = FALSE}
cat("<div id=\"tbl:supTab_SAcounts\">")
supTab_SAcounts_cap <- supTab_cap(name='supTab_SAcounts', caption =  'Counts for number of studies with cell types labels before and after cell type label transfer')

fontsize(saTable  %>% padding(padding = 5, part = "body") %>% align(align = 'center', part = 'all'), size = 8, part = 'all') 
#Output Caption (* * for italics)
cat(paste0("\n*",supTab_SAcounts_cap,"*\n"))
# Output </div>
cat("</div>")
```

```{r supTab_links, fig.width=3, fig.height=6, out.width=600, echo = F, results='asis', warning = F, fig.cap = supTab_links_cap, fig.pos = 'H'}
supTab_links_cap <- supTab_cap(name='supTab_links', caption =  'Links to code and resources')
cat("<div id=\"tbl:supTab_links\">")

linksTable <- tibble::tribble(
                                           ~`Resource or File`,                                                                         ~Link,  ~Accession,
                                             "Seurat Object", "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/scEiaD_all_seurat_v3.Rdata",          NA,
                                            "Anndata Object",    "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/scEiaD_all_anndata.h5ad",          NA,
                                   "Counts, R sparse matrix",               "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/counts.Rdata",          NA,
                                       "Cell level metadata",     "http://hpc.nih.gov/~mcgaugheyd/scEiaD/2021_03_17/metadata_filter.tsv.gz",          NA,
                              "Codebase for scEiaD creation",                                           "https://github.com/davemcg/scEiaD",   "ffdf738",
                            "Codebase for scEiad manuscript",                                "https://github.com/davemcg/scEiaD_manuscript",          NA,
                "Zenodo deposit of all above files and code",                                                      "https://zenodo.org/record/5129265",   "5129265",
                            "iPSC RPE scRNA Raw Fastq Files",                "https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE180662", "GSE180662"
                )
fontsize(flextable(linksTable)  %>% padding(padding = 5, part = "all") %>% align(align = 'left', part = 'all'), size = 8, part = 'all') %>% autofit() %>% fit_to_width(7)
#Output Caption (* * for italics)
cat(paste0("\n*",supTab_links_cap,"*\n"))
# Output </div>
cat("</div>")
```
